### 2018-11-29 2018_nips_vigil_poster/main.tex
Rename Summary to Contributions.
Increased size of Fig. 3.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Summary}{name=summary,column=0,row=0}{
\begin{itemize}
	\compresslist
	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
	\item[$\bullet$] We evaluate the MAC model and the simplified variant on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can reduce a model's accuracy.

@@

\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=mac-model, column=0, below=summary}{
	\vspace{-10pt}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
		\caption{The MAC cell, based on~\cite{hudson2018compositional}.}
		\label{fig:mac_cell}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item[$\bullet$] MAC network: a recurrent model performing sequential reasoning. At each step, it analyzes the question and shifts the attention over the image.
		\item[$\bullet$] Recurrent MAC cell: consists of a control unit, a read unit \& a write unit. The control unit updates the control state $c_i$ \& drives the attention over the question words.
		\item[$\bullet$] The read unit, guided by $c_i$ extracts information from the image. The write unit uses this information to update the memory state $m_i$.
	\end{itemize}
}

@@

\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
		\caption{\textit{How many objects are either small cylinders or red things?} -- Answer: 5.}
		\label{fig:clevr_task}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
	  	\compresslist
	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
	\end{itemize}
	\vspace{-10pt}
	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Compositional generalization of the MAC model}{name=mac-failures, column=1, below=experiments}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.60\textwidth]{../img/fail_mac_cogent_b_shape.png}
		\caption{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}
		\label{fig:mac_failure}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item[$\bullet$] Asked about the shape of the leftmost \textbf{gray cylinder}, the model correctly finds it, (cf. \emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \textbf{gray cylinders} during training, but saw \textbf{gray cubes}.
		\item[$\rightarrow$] This indicates that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
	\end{itemize}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Contributions}{name=contributions,column=0,row=0}{
\begin{itemize}
	\compresslist
	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model~\cite{hudson2018compositional}, which achieves comparable accuracy while training \emph{\textbf{faster}}.
	\item[$\bullet$] We evaluate the MAC model and the simplified variant on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can reduce a model's accuracy.

@@

\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=mac-model, column=0, below=contributions}{
	\vspace{-10pt}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.33\textwidth]{../img/mac_cell.pdf}
		\caption{The MAC cell, based on~\cite{hudson2018compositional}.}
		\label{fig:mac_cell}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item[$\bullet$] MAC network: a recurrent model performing sequential reasoning. At each step, it analyzes the question and shifts the attention over the image.
		\item[$\bullet$] Recurrent MAC cell: consists of a control unit, a read unit \& a write unit. The control unit updates the control state $c_i$ \& drives the attention over the question words.
		\item[$\bullet$] The read unit, guided by $c_i$ extracts information from the image. The write unit uses this information to update the memory state $m_i$.
	\end{itemize}
}

@@

\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
		\caption{\textbf{Q}: \textit{How many objects are either small cylinders or red things?} -- \textbf{A}: 5.}
		\label{fig:clevr_task}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
	  	\compresslist
	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
	\end{itemize}
	\vspace{-10pt}
	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Compositional generalization of the MAC model}{name=mac-failures, column=1, below=experiments}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.71\textwidth]{../img/fail_mac_cogent_b_shape.png}
		\caption{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}
		\label{fig:mac_failure}
	\end{figure}
	\vspace{-20pt}
	\begin{itemize}
		\compresslist
		\item[$\bullet$] Asked about the shape of the leftmost \textbf{gray cylinder}, the model correctly finds it, (cf. \emph{visual attention map}), and refers to it using its color (\emph{attention over the question words}).
		\item[$\bullet$] Yet, predicts the shape as \textbf{cube}, as it never saw \textbf{gray cylinders} during training, but saw \textbf{gray cubes}.
		\item[$\rightarrow$] This indicates that MAC does not separate shape from color, but has a better understanding of colors (as found the object by its color).
	\end{itemize}
}
